Report on practical exercises for \emph{Music Similarity and Retrieval: Content- and Context-based Approaches}

### 2015-10-21 report/msrcc-report.tex
beautify report

% \keywords{TODO, TODO, TODO}

\begin{bottomstuff}
This is a lot of bottom stuff.
\end{bottomstuff}

\maketitle

@@

    for _artist in range(0, MAX_ARTISTS):
        artist_list.append((json_content["artists"]["artist"][_artist]["name"]).encode("utf-8"))

@@

        for _user in range(0, MAX_FANS):
            user_list += (json_content["topfans"]["user"][_user]["name"]).encode("utf-8") + '\n'

@@

    # recommend artists
    recommended_artists_idx = [not_listened[randint(0,len(not_listened)-1)] for _ in range(num_recommend)]

@@

    # Select the k closest neighbor to seed user (which is the last but one; last one is user u herself!)
    kneighbor_idx = sort_idx[-(1+K):-1]

>>>>

\begin{bottomstuff}
\end{bottomstuff}
\maketitle

@@

    for _artist in range(0, MAX_ARTISTS):
        artist_list.append((json_content["artists"]["artist"][_artist]["name"]) \ 
        .encode("utf-8"))

@@

        for _user in range(0, MAX_FANS):
            user_list += (json_content["topfans"]["user"][_user]["name"]) \ 
            .encode("utf-8") + '\n'

@@

    # recommend artists
    recommended_artists_idx = [not_listened[randint(0,len(not_listened)-1)] \
     for _ in range(num_recommend)]

@@

    # Select the k closest neighbor to seed user 
    # (which is the last but one; last one is user u herself!)
    kneighbor_idx = sort_idx[-(1+K):-1]
